This is an example of article title

### 2019-08-13 paper/paper.tex
Updates from Overleaf
- Added brief explanation of the `fit` method - Added a note about how to install the package

@@

Community contributions and feedback are highly encouraged in order to best continue developing the project. Some features I would like the project to support in the future include more advanced estimators such as: (1) choice-variant categorical response models, (2) count/rate models such as zero-inflated, and (3) censored/truncated response models. Econometrics.jl is ISC licensed and available at the GitHub repository.

>>>>

The syntax to estimate a model follows the StatsBase API which provides two methods for building and estimating models (i.e., \textit{fit} and \textit{fit!}). The \textit{fit} approach takes (1) an estimator, (2) a model formula, (3) data, and additional arguments depending on the model. \textit{EconometricModel} is the generic estimator which dispatches to continuous, nominal or ordinal response models automatically based on the type of the response. Other estimators are available and the following figures illustrate some of the use cases.

@@

Community contributions and feedback are highly encouraged in order to best continue developing the project. Some features I would like the project to support in the future include more advanced estimators such as: (1) choice-variant categorical response models, (2) count/rate models such as zero-inflated, and (3) censored/truncated response models. Econometrics.jl is ISC licensed and available at the GitHub repository. The package is registered in the official Julia registry (General); as such it can be installed using the Julia package manager.
